% LaTeX file for resume 
% This file uses the resume document class (res.cls)

\documentclass[margin]{res} 
% the margin option causes section titles to appear to the left of body text 
% \topmargin=-0.25in
% \oddsidemargin -.5in
% \evensidemargin -.5in
% \textwidth=6.0in
% \itemsep=-0.9in
% \parsep=-0.9in

\usepackage[margin=.9in]{geometry}
\geometry{a4paper,scale=1}
% \geometry{a4paper,left=2cm,right=2cm,top=2cm,bottom=1cm}

\textwidth=5.2in % increase textwidth to get smaller right margin
% \usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
% \usepackage{newcent}   % uses new century schoolbook postscript font
% \usepackage{fontaxes,mweights,ebgaramond} % uses EB garamond font
\renewcommand{\sfdefault}{lmr}

% Palatino font
% \usepackage{mathpazo}
% \usepackage{microtype}

% Chinese
\usepackage{fontspec}
\usepackage[slantfont, boldfont]{xeCJK}
\setCJKmainfont{STSongti-SC-Light}
\XeTeXlinebreaklocale "zh"
\XeTeXlinebreakskip = 0pt plus 1pt

\usepackage{hyperref}
\usepackage[dvipsnames]{xcolor}
\hypersetup{
    colorlinks=true,
    linkcolor=NavyBlue,
    filecolor=NavyBlue,      
    urlcolor=NavyBlue,
    citecolor=NavyBlue,
}




\begin{document} 

\name{郭鹏辉 · Penghui Guo\\[20pt]} % the \\[12pt] adds a blank line after name
\address{
Nanjing University of Aeronautics and Astronautics (NUAA) \\
29 Jiangjun Avenue  \\
Nanjing Jiangsu, 211106 China}
\address{
Email: \hfill guopenghui@outlook.com \\
Homepage: \hfill https://guo.ph \\
Updated: \hfill 2021-04-25 \\[15pt]
}

\begin{resume} 





\section{\sc Education}

{\bf Ph.D. Candidate,}  Management Science and Engineering \hfill Apr. 2019 - present\\
{\bf Nanjing University of Aeronautics and Astronautics} \hfill Nanjing, China
\begin{itemize}  \itemsep -2pt  % reduce space between items
\item[\(\circ\)] Advisor: Prof. Jianjun Zhu
\item[\(\circ\)] College of Economics and Management
\item[\(\circ\)] Concentrations: Disaster and Emergency Operations Management
\end{itemize} \vspace{-.5em}

{\bf Visiting Student,} Industrial Engineering \hfill Sep. 2019 - Dec. 2019\\
{\bf Texas State University} \hfill San Marcos, U.S.
\begin{itemize}   \itemsep -2pt  % reduce space between items
\item[\(\circ\)] Advisor: Dr. Zhijie (Sasha) Dong
\item[\(\circ\)] UTIL Lab at Ingram School of Engineering (https://dong.wp.txstate.edu/)
\item[\(\circ\)] Research project: {\it A stochastic optimization approach for prepositioning relief supplies considering lateral transshipment\(^{[3]}\)} . 
\item[\(\circ\)] Funded by Nanjing University of Aeronautics and Astronautics.
\end{itemize}\vspace{-.5em}

{\bf M.S.,}  Management Science and Engineering \hfill Sep. 2016 - Apr. 2019 \\
{\bf Nanjing University of Aeronautics and Astronautics} \hfill Nanjing, China
\begin{itemize}  \itemsep -2pt  % reduce space between items
\item[\(\circ\)] Advisor: Prof. Jianjun Zhu
\item[\(\circ\)] College of Economics and Management
\item[\(\circ\)] Dissertation: {\it Models and Algorithms for Post Disaster Rescue Route Optimization}, click \href{https://docs.google.com/viewer?url=https://github.com/phguo/phguo.github.io/raw/master/full_text/zh-MasterThesis.pdf}{here} for full text.
\end{itemize}\vspace{-.5em}

{\bf B.S.,}  Industrial Engineering \hfill Sep. 2011 - Jul. 2015 \\
{\bf Henan Polytechnic University} \hfill Jiaozuo, China
\begin{itemize}   \itemsep -2pt  % reduce space between items
\item[\(\circ\)] School of Energy Science and Engineering
\item[\(\circ\)] Dissertation: {\it Analysis and Optimization of the Production Organization Process of a Beverage Manufacturer}
\end{itemize}





\section{\sc Research \\Interests}

$\bullet$ {\bf Disaster and Emergency Operations Management:} mathematical modeling in disasters and public emergencies operations management incorporating the uncertainty. \\
$\bullet$ {\bf Optimization Modeling and Algorithms:} especially stochastic optimization and integer optimization. \\
$\bullet$ {\bf Data-driven modeling in the public-health emergency.}





\section{\sc Skills}

50k+ lines of code in {\bf Python} (including the package {\it gurobipy} for interacting with {\bf Gurobi}, {\it Pyomo} for optimization modeling, {\bf Matplotlib} for scientific visualization, and {\it Django} for web development). 
Solid knowledge of modeling and algorithms for deterministic integer programming and {\bf stochastic programming}. 
Working proficiency in typesetting by \LaTeX. Native in Chinese Mandarin.





\section{\sc Research Experience}

\textbf{{Integrated Optimization for Large-scale Natural Disaster Emergency Rescue Location-Routing-Allocation Problem}} \hspace{68pt} Jun. 2017 - Nov. 2018
\begin{itemize} \itemsep -2pt  % reduce space between items
\item[\(\circ\)] Project supported by {\it Foundation of Graduate Innovation Center in Nanjing University of Aeronautics and Astronautics}.
\end{itemize}




\section{\sc Publications}

[3] \textbf{Guo,P.,} Dong,Z.S.*, Zhu,J., Hu,S.(working paper). The Nested Logic-based Benders Decomposition for Stochastic Disaster Response Planning with Inter-facility Coordination.
\begin{itemize} \itemsep -2pt  % reduce space between items
\item[\(\circ\)] Methodology: two-stage stochastic programming, vehicle routing problem, (nested) logic-based Benders decomposition.
\end{itemize} \vspace{-.5em}

[2] \textbf{Guo,P.,} Zhu,J.*, Wang,H.(2019). Location-routing-allocation Problem with Consolidated Shipping of Heterogeneous Relief Supplies in Post-disaster Rescue. \textit{Systems Engineering - Theory \& Practice,} 39(9),2345-2360. (Chinese journal, click \href{https://docs.google.com/viewer?url=https://github.com/phguo/phguo.github.io/raw/master/full_text/zh-LocationRoutingAllocation.pdf}{here} for full text.)

[1] \textbf{Guo,P.,} Zhu,J.*, Wang,H.(2018). Multi-location Emergency Rescue Route Optimization under the Condition of Natural Disaster Considering Safety and Time Cost. \textit{Systems Engineering,} 36(6),62-70. (Chinese journal, click \href{https://docs.google.com/viewer?url=https://github.com/phguo/phguo.github.io/raw/master/full_text/zh-RiskTime.pdf}{here} for full text.) 

% \textit{(* represents the corresponding author)}





\section{\sc Honors \\and Awards}

$\bullet$ {\bf 2\(^{nd}\) Price}, the 2\(^{nd}\) National Innovation Competition of Industrial Engineering and Lean Management ({\bf top 3\%} of participants) \hfill May 2019 
\begin{itemize}  \itemsep -2pt  % reduce space between items
\item[\(\circ\)] Name of the Project: \textit{Models and Algorithms for Emergency Rescue Location-Routing Optimization with Stochastic Demand}
\end{itemize} \vspace{-1em}

$\bullet$ {\bf Outstanding Postgraduate Student} of Nanjing University of Aeronautics and Astronautics (top 20\% of postgraduate student) \hfill Jul. 2019 \\
$\bullet$ {\bf 3\(^{rd}\) Price}, the 15\(^{th}\) China Post-Graduate Mathematical Contest in Modeling (top 30\% of participants) \hfill Dec. 2018 \\
$\bullet$ {\bf National Scholarship} for Graduate Students by Ministry of Education of the P.R.C ({\bf top 0.5\%} of graduate student) \hfill Oct. 2018 \\
$\bullet$ {\bf 3\(^{rd}\) Price}, the 2018 NUAA Post-Graduate Mathematical Contest in Modeling (top 30\% of participants) \hfill Jun. 2018 \\
$\bullet$ {\bf 3\(^{rd}\) Price}, the 14\(^{th}\) China Post-Graduate Mathematical Contest in Modeling (top 30\% of participants) \hfill Dec. 2017





\section{\sc Open Source Activities} 

\textbf{{VRP2E }} https://github.com/phguo/VRP2E \hfill Jan. 2018
\begin{itemize} \itemsep -2pt
\item[\(\circ\)] A coevolutionary-algorithm solver for multi-objective two-echelon vehicle routing problems.
\end{itemize} \vspace{-.5em}
\textbf{{LRP2E-instances }} https://github.com/phguo/LRP2E-instances \hfill Jan. 2018
\begin{itemize} \itemsep -2pt
\item[\(\circ\)] Instances data for 2-echelon vehicle routing problem (VRP2E) with resource constraints. 
\end{itemize}


\end{resume} 
\end{document} 
