% !TEX program = xelatex
% LaTeX file for resume 
% This file uses the resume document class (res.cls)

\documentclass[margin]{res} 
% the margin option causes section titles to appear to the left of body text 
% \topmargin=-.4in
% \oddsidemargin -.5in
% \evensidemargin -.5in
% \textwidth=6.0in
% \itemsep=-0.9in
% \parsep=-0.9in

% \usepackage[margin=.9in]{geometry}
% \geometry{a4paper,scale=1}
% \geometry{a4paper,left=2cm,right=2cm,top=2cm,bottom=1cm}

\textwidth=5.2in % increase textwidth to get smaller right margin
% \usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
% \usepackage{newcent}   % uses new century schoolbook postscript font
% \usepackage{mweights} % uses EB garamond font
% \renewcommand{\sfdefault}{lmr}


% Palatino font 
% \usepackage{mathpazo}
% \usepackage{microtype}

% Chinese
\usepackage{fontspec} 
\usepackage[slantfont, boldfont]{xeCJK}
\setCJKmainfont{STSongti-SC-Light}
\XeTeXlinebreaklocale "zh"
\XeTeXlinebreakskip = 0pt plus 1pt

\usepackage{hyperref}
\usepackage[dvipsnames]{xcolor}
\hypersetup{
    colorlinks=true,
    linkcolor=NavyBlue,
    filecolor=NavyBlue,
    urlcolor=NavyBlue,
    citecolor=NavyBlue,
}

\usepackage{fancyhdr}
\pagestyle{plain}


\begin{document} 


\name{郭鹏辉 ·  Penghui Guo\\[5pt]} % the \\[12pt] adds a blank line after name
\address{\\ [5pt]
Nanjing University of Aeronautics and Astronautics (NUAA) \\
29 Jiangjun Avenue  \\
Nanjing Jiangsu, 211106 China}
\address{\small \it
\hfill Updated: \today \\ [5pt]
Email: \hfill m@guo.ph \\
Homepage: \hfill \href{https://guo.ph}{https://guo.ph} \\[5pt]
}


\begin{resume} 


\vspace{-.8em}
\section{\sc Education}


{\bf Ph.D.,}  Management Science and Engineering \hfill {\it Apr. 2019 - Oct. 2024}\\
{\bf Nanjing University of Aeronautics and Astronautics} \hfill Nanjing, China
\begin{itemize}  \itemsep -2pt  % reduce space between items
\item[\(-\)] Advisor: Prof. Jianjun Zhu
\item[\(-\)] College of Economics and Management
\item[\(-\)] Dissertation: Optimal Preparation and Distribution of Humanitarian Supplies by Stochastic Programming and Decomposition Algorithms.
\end{itemize}
\vspace{-.8em}


{\bf Visiting Student,} Industrial Engineering \hfill {\it Sep. 2019 - Dec. 2019}\\
{\bf Texas State University} \hfill San Marcos, U.S.
\begin{itemize}   \itemsep -2pt  % reduce space between items
\item[\(-\)] Advisor: Prof. Zhijie Sasha Dong
\item[\(-\)] UTIL Lab at Ingram School of Engineering
\item[\(-\)] Research project: A Stochastic Optimization Approach for Prepositioning Relief Supplies Considering Lateral Transshipment
\item[\(-\)] Funded by NUAA
\end{itemize}
\vspace{-.8em}

{\bf M.S.,}  Management Science and Engineering \hfill {\it Sep. 2016 - Apr. 2019}\\
{\bf Nanjing University of Aeronautics and Astronautics} \hfill Nanjing, China
\begin{itemize}  \itemsep -2pt  % reduce space between items
\item[\(-\)] Advisor: Prof. Jianjun Zhu
\item[\(-\)] College of Economics and Management
\item[\(-\)] Dissertation: Models and Algorithms for Post Disaster Rescue Route Optimization. (\href{https://docs.google.com/viewer?url=https://github.com/phguo/phguo.github.io/raw/master/full_text/zh-MasterThesis.pdf}{full text})
\end{itemize}
\vspace{-.8em}

{\bf B.S.,}  Industrial Engineering \hfill {\it Sep. 2011 - Jul. 2015} \\
{\bf Henan Polytechnic University} \hfill Jiaozuo, China
\begin{itemize}   \itemsep -2pt  % reduce space between items
\item[\(-\)] School of Energy Science and Engineering
% \item[\(-\)] Dissertation: {\it Analysis and Optimization of the Production Organization Process of a Beverage Manufacturer}
\end{itemize}


\vspace{-.8em}
\section{\sc Research \\Interests}


$\diamond$ {\bf Disaster and Humanitarian Operations Management:} The location, routing, and allocation problem for humanitarian planning and response. \\
$\diamond$ {\bf Optimization Modeling and Algorithms:} Stochastic programming, mixed-integer programming, and decomposition algorithms. Development for optimization packages.


\vspace{-.8em}
\section{\sc Skills}


Solid knowledge of modeling and algorithms for optimization problems. 
50k+ lines of \texttt{Python} code (including \texttt{gurobipy} for \texttt{Gurobi}, \texttt{Pyomo} for optimization modeling, \texttt{Matplotlib} for visualization, and \texttt{Django} for web development). 
Beginner of \texttt{Julia}.
Working proficiency in typesetting by \LaTeX. Native in Chinese Mandarin.


\vspace{-.8em}
\section{\sc Research \\Papers}


% [4] \textbf{Guo,P.}, Dong,Z.S.*, \& Zhu,J. (working paper). Nested logic-based Benders decomposition for disaster preparedness planning with horizontal coordination.
% \vspace{-.8em}

[4] \textbf{Guo,P.}, Dong,Z.S.*, \& Zhu,J. (2025). Nested logic-based Benders decomposition for disaster preparedness planning with horizontal coordination. \textit{IISE Transactions}. \url{https://doi.org/10.1080/24725854.2025.2491495}. (\href{https://guo.ph/publication/LateralTransshipment2025.pdf}{preprint})
\vspace{-.8em}

[3] \textbf{Guo,P.}, \& Zhu,J.* (2023). Capacity reservation for humanitarian relief: A logic-based Benders decomposition method with subgradient cut. \textit{European Journal of Operational Research}, 311(3), 942-970. \url{https://doi.org/10.1016/j.ejor.2023.06.006}. (\href{https://guo.ph/publication/CapacityReservationHumanitarian2023.pdf}{preprint})
\vspace{-.8em}

[2] \textbf{Guo,P.}, Zhu,J.*, \& Wang,H. (2019). Location-routing-allocation problem with consolidated shipping of heterogeneous relief supplies in post-disaster rescue. \textit{Systems Engineering - Theory \& Practice,} 39(9), 2345-2360. (in Chinese, \href{https://guo.ph/publication/zh-LocationRoutingAllocation.pdf}{preprint})
\vspace{-.8em}

[1] \textbf{Guo,P.}, Zhu,J.*, \& Wang,H. (2018). Multi-location emergency rescue route optimization under the condition of natural disaster considering safety and time Cost. \textit{Systems Engineering,} 36(6), 62-70. (in Chinese, \href{https://guo.ph/publication/zh-RiskTime.pdf}{preprint})

\vspace{-.8em}
\section{\sc Research Experience}


{\sc Academic}
\vspace{-.8em}

\textbf{{Integrated Optimization for Large-scale Natural Disaster Emergency Rescue Location-Routing-Allocation Problem}} \hspace{65pt} {\it Jun. 2017 - Nov. 2018}
\begin{itemize} \itemsep -2pt  % reduce space between items
\item[\(-\)] Project supported by {Foundation of Graduate Innovation Center in NUAA}.
\end{itemize}


\vspace{-.8em}
\section{\sc Scholarships, \\Honors, \\and Awards}


{Short-term visiting Ph.D. scholarship} \hfill {\it Jun. 2019}
\begin{itemize} \itemsep -2pt  % reduce space between items
\item[\(-\)] Supported by NUAA for three months.
\end{itemize}
\vspace{-.8em}

{2\(^{nd}\) Price} (top 3\% of participants)   \hfill {\it May 2019}
\begin{itemize} \itemsep -2pt  % reduce space between items
\item[\(-\)] The 2\(^{nd}\) National Innovation Competition of Industrial Engineering and Lean Management.
\item[\(-\)] Name of the Project: {Models and Algorithms for Emergency Rescue Location-Routing Optimization with Stochastic Demand}
\end{itemize}
\vspace{-.8em}

{Outstanding Postgraduate Student} (top 20\% of postgraduate student) \hfill {\it Apr. 2019}
\begin{itemize} \itemsep -2pt  % reduce space between items
\item[\(-\)] By NUAA graduate school.
\end{itemize}
\vspace{-.8em}

{3\(^{rd}\) Price} (top 30\% of participants)   \hfill {\it Dec. 2018}
\begin{itemize} \itemsep -2pt  % reduce space between items
\item[\(-\)] The 15\(^{th}\) China Post-Graduate Mathematical Contest in Modeling.
\end{itemize}
\vspace{-.8em}

{\bf National Scholarship} (top 0.5\% of graduate student) \hfill {\it Oct. 2018}
\begin{itemize} \itemsep -2pt  % reduce space between items
\item[\(-\)] By Ministry of Education of the People's Republic of China.
\end{itemize}
\vspace{-.8em}

{3\(^{rd}\) Price} (top 30\% of participants)  \hfill {\it Jun. 2018} 
\begin{itemize} \itemsep -2pt  % reduce space between items
\item[\(-\)] The 2018 NUAA Post-Graduate Mathematical Contest in Modeling.
\end{itemize}
\vspace{-.8em}

% $\diamond$ 
{3\(^{rd}\) Price} (top 30\% of participants)  \hfill {\it Dec. 2017}
\begin{itemize} \itemsep -2pt  % reduce space between items
\item[\(-\)] The 14\(^{th}\) China Post-Graduate Mathematical Contest in Modeling.
\end{itemize}


\vspace{-.8em}
\section{\sc Open Source Activities} 


\textbf{Benders.jl } https://github.com/phguo/Benders.jl \hfill {\it May 2022 - present}
\begin{itemize} \itemsep -2pt
\item[\(-\)] A Julia package for Benders decomposition and its variants (now support the classical Benders).
\end{itemize}
\vspace{-.8em}

\textbf{BendersLib } https://pypi.org/project/BendersLib \hfill {\it Jun. 2021 - present}
\begin{itemize} \itemsep -2pt
\item[\(-\)] A Python library for Benders decomposition (under development).
\end{itemize}
\vspace{-.8em}

\textbf{VRP2E } https://github.com/phguo/VRP2E \hfill {\it Jan. 2018}
\begin{itemize} \itemsep -2pt
\item[\(-\)] A coevolutionary-algorithm solver for multi-objective two-echelon vehicle routing problems.
\end{itemize}
\vspace{-.8em}

\textbf{arxiv-latex-cleaner } https://pypi.org/project/arxiv-latex-cleaner \hfill {\it Jan. 2022}
\begin{itemize} \itemsep -2pt
\item[\(-\)] Contributor.
\item[\(-\)] A 3k+ stars tool that cleans the LaTeX code for submitting to arXiv.
\end{itemize}


\vspace{-.8em}
\section{\sc Membership}


\textbf{INFORMS Student Member} (ID: 1606090) \hfill {\it Apr. 2021 - present}
\begin{itemize}  \itemsep -2pt
\item[\(-\)] The Institute for Operations Research and the Management Sciences (INFORMS)
\end{itemize} 
\vspace{-.8em}

\textbf{ORSC Student Member} (ID: S390022695M) \hfill {\it Oct. 2021 - present}
\begin{itemize}  \itemsep -2pt
\item[\(-\)] The Operations Research Society of China (ORSC)
\end{itemize}
\vspace{-.8em}

\textbf{SESC Member} \hfill {\it Oct. 2021 - present}
\begin{itemize}  \itemsep -2pt
\item[\(-\)] The System Engineering Society of China (SESC)
\end{itemize}
\vspace{-.8em}

\textbf{SCOPE  Student Member} (ID: S320005073A) \hfill {\it Oct. 2021 - present}
\begin{itemize}  \itemsep -2pt
\item[\(-\)] Chinese Society of Optimization, Overall Planning and Economic Mathematics (SCOPE)
\end{itemize}



\end{resume} 
\end{document} 
